Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-04 paper/main.tex
main tex

\usepackage[T1]{fontenc} 
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
% \bibliographystyle{IEEEtran} 
% \usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
% \addbibresource{main.bib}

@@

\subsection{Open Nighttime Lights}
% this is the explaination  \cite{BARA2020106658}

@@

\subsection{nginx/tomcat}
Nginx

\subsection{RDS/Lambda/secrets manager/SQS/EC2}
this is the explanation

@@

% \printbibliography

>>>>

\usepackage[T1]{fontenc} 
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
\bibliographystyle{IEEEtran} 
\usepackage[backend=bibtex,doi=true, natbib=true ]{biblatex}
\addbibresource{main.bib}

@@

\subsection{Open Nighttime Lights}
this is the explaination  \cite{BARA2020106658}

@@

\subsection{nginx/tomcat}
Nginx is the widely used web server all over the world. It also has the excellent performance as a reverse proxy. We use it as our fontend server. Tomcat is a tranditional Java web container supporting Java Servlet. Our Java code run on Tomcat.

\subsection{RDS/Lambda/secrets manager/SQS/EC2}
These items are the name of services on AWS. Especially, we use Lambda to generate temperary password of RDS, and store it in Secrets Manager. It is a good method to enhance the security of database password.

@@

\printbibliography
